%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {B.S. in Computer Science} % Degree
    {Instituto de Matemática e Estatística - Universidade de São Paulo (IME-USP)} % Institution
    {São Paulo/SP, Brazil} % Location
    {Jan. 2013 - Dez. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {I contributed to the Mezuro project at CCSL as a software engineer intern, enhancing a social network platform for code quality assessment.}
        \item {I have completed a research project on the actor model, which focused on concurrent programming and resource sharing.}
        \item {I led technological initiatives as the Technology Director at IME Jr., managing crowdfunding for academic and extension groups.}
        \item {I guided undergraduate and graduate students on XP practices as an Agile Coach in the Extreme-Programming Laboratory Course.}
      \end{cvitems}
    }
  \newline
  \cventry
    {Advanced Training in Complex Data Mining} % Degree
    {Instituto de Computação - Universidade Estadual de Campinas (IC-UNICAMP)} % Institution
    {Campinas/SP, Brazil} % Location
    {Jan. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Acquired extensive hands-on experience in R and Python, applying deep learning, artificial intelligence, and both classic and cutting-edge machine learning techniques to complex data mining challenges.}
        \item {Applied deep learning and computer vision techniques in the Kaggle Contest: CV Cataract Detection, achieving results that outperformed specialist-level accuracy with high confidence.}
      \end{cvitems}
    }
  \newline
  \cventry
    {MBA in Software Technology} % Degree
    {Escola Politécnica - Universidade de São Paulo (Poli-USP)} % Institution
    {São Paulo, Brazil} % Location
    {Jan. 2021 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Completed coursework in advanced software engineering topics, including software architecture, agile methodologies, and project management, as part of the MBA program at Escola Politécnica of USP.}
        \item {Gained in-depth knowledge in software quality assurance, systems integration, and cloud computing.}
        \item {Conducted research on the software delivery lifecycle, focusing on Continuous Integration, Deployment, Delivery, and Monitoring.}
        \item {Dropped out before completing the final thesis, having successfully completed all core courses.}
      \end{cvitems}
    }
  \newline
  \cventry
    {M.S. in Computer Science} % Degree
    {Instituto de Matemática e Estatística - Universidade de São Paulo (IME-USP)} % Institution
    {São Paulo/SP, Brazil} % Location
    {Aug. 2024 - Dez. 2028} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Current Studies: Actively engaged in courses like HCI Principles, where I explore the intricacies of Human-Computer Interaction, and Model Based Testing, focusing on leveraging formal methods to enhance software reliability and testing efficiency.}
        \item {Research Interests: Passionately pursuing research in Haskell, Ada, and Formal Verification, with a keen interest in Compilers Design and Optimization, Theory of Computing, and Functional Programming. My work delves into Logic, Lambda Calculus, and Artificial Inteligence, with a strong emphasis on applying these principles to optimize programming languages and complex software systems.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
