%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Professor of Computer Science} % Job title
    {FIAP} % Organization
    {São Paulo, Brazil} % Location
    {September 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching undergraduate courses, with a focus on Domain Driven Design using Java.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Chief Severino da Oficina (CSO) / Professor of Computer Science} % Job title
    {Binary Forge IT} % Organization
    {São Paulo, Brazil} % Location
    {August 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Founded and led Binary Forge IT, focusing on consulting and educational projects in programming and software development.}
        \item {Specialized in teaching and consulting on artificial intelligence, machine learning, data science, and DevOps.}
        \item {Delivered training on industry-standard practices like Test-Driven Development (TDD), Behavior-Driven Development (BDD), and Clean Architecture.}
        \item {Developed and conducted courses on multiple programming languages, including Java, Python, R, and JavaScript.}
        \item {Utilized modern frameworks like Spring, Docker, and Kubernetes for teaching and consulting.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Senior Software Engineering Consultant} % Job title
    {Campspot} % Organization
    {Grand Rapids, Michigan, United States} % Location
    {June 2023 - December 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the development and implementation of software systems focused on campground administration, reservation management, and third-party integrations.}
        \item {Improved customer experience and operational efficiency through user-centric software solutions.}
        \item {Collaborated with cross-functional teams for seamless deployment and system optimization.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Technical Lead} % Job title
    {Zup Innovation} % Organization
    {Campinas, São Paulo, Brazil} % Location
    {April 2023 - June 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led technical direction for a Bank as a Service (BaaS) platform, focusing on financial product integration and optimization.}
        \item {Conducted regular team meetings to foster a supportive and productive team environment.}
        \item {Developed and maintained technical documentation and aligned technical solutions with business goals.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Staff Software Engineer} % Job title
    {Zup Innovation} % Organization
    {Campinas, São Paulo, Brazil} % Location
    {August 2022 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Benchmarked Bank as a Service (BaaS) offerings against industry standards to improve financial products.}
        \item {Collaborated with solution architects and cloud engineers to scale and secure public cloud infrastructure.}
        \item {Ensured the platform's sandbox environment met diverse developer client needs.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Senior Software Developer - Platform Engineer} % Job title
    {Vinta Software} % Organization
    {Brazil} % Location
    {February 2022 - August 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led platform improvements, infrastructure enhancement, and process optimization for a docketing platform used by thousands of law firms.}
        \item {Authored system documentation and RFCs, and mentored young developers.}
        \item {Introduced innovative microservices management techniques using Azure public cloud services.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineer} % Job title
    {Zé Delivery} % Organization
    {São Paulo, São Paulo, Brazil} % Location
    {September 2020 - February 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-founded the logistics optimization team, using AWS Lambda to streamline delivery logistics.}
        \item {Implemented data-driven and event-driven systems that optimized delivery groupings.}
        \item {Integrated machine learning APIs into delivery operations to improve efficiency.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Independent Tech Instructor} % Job title
    {Grupo Alura} % Organization
    {São Paulo, Brazil} % Location
    {August 2020 - February 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed technical teaching materials, scripts, and video lectures for Java Unit Testing courses.}
        \item {Continuously updated course materials and provided consultancy for the development of new technology courses.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Technical Instructor and Java Specialist} % Job title
    {Grupo Alura} % Organization
    {São Paulo, Brazil} % Location
    {March 2019 - September 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led Java programming courses on backend development, security, and DevOps.}
        \item {Created and continuously updated teaching materials for in-company and online courses.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Full Stack Developer} % Job title
    {Grupo Alura} % Organization
    {São Paulo, Brazil} % Location
    {November 2017 - March 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and enhanced online learning platforms and internal systems for payments, analytics, and marketing.}
        \item {Managed the full lifecycle of software development using Java, Spring Framework, Ruby on Rails, and AWS.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineer Trainee} % Job title
    {Avenue Code} % Organization
    {São Paulo, Brazil} % Location
    {July 2016 - November 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Rotated through key areas: Quality Assurance, Ruby on Rails development, Java development, and Vanilla Frontend development.}
        \item {Led public lectures and coding events to foster collaboration and knowledge sharing.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineer Intern} % Job title
    {Medicinia} % Organization
    {São Paulo, Brazil} % Location
    {December 2014 - July 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to software development projects, client requirement discussions, and project management using Trello and Agile methodologies.}
        \item {Developed software using Ruby on Rails, Java, and JavaScript frameworks.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineer Intern} % Job title
    {Nextar} % Organization
    {São Paulo, Brazil} % Location
    {June 2014 - December 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed real-time solutions for small business data integration and payment functionalities using Ruby on Rails, MySQL, and RESTful APIs.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineer Intern} % Job title
    {FLOSS Competence Center of the University of São Paulo} % Organization
    {São Paulo, Brazil} % Location
    {October 2013 - June 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to open-source projects, using Test-Driven Development (TDD) and Behavior-Driven Development (BDD).}
        \item {Worked on Mezuro, a web platform designed to collect, analyze, and interpret source code metrics.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
